```{r}
REMOVE ME BEFORE KNITTING!
```
---
title: "Assignment 3"
author: "Lacey Hartigan"
date: "due 2/9/21"
output:
  pdf_document: default
---

Use the attrition dataset to answer the following questions. As always, your
assignment must be turned in as a .Rmd file (and also please upload a knit file - html or PDF)

First code chunk - set the file structure and open your libraries. 
```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```

## 1. Create a plot that shows the distribution of monthly income. Write a sentence or two desribing what the plot tells you about the data. 
*Please put your sentence(s) for each question OUTSIDE of your code chunks.*
```{r}

``` 

## 2. Create a plot that shows the average level of monthly income by field of education. Write a sentence or two desribing what the plot tells you about the data. 
```{r}

```

## 3. Create another plot that shows average level of monthly income by field of education and gender. Write a sentence or two desribing what the plot tells you about the data. 
```{r}

```

## 4. Create a plot that shows average levels of monthly income by field of education, gender and job level (note - this is on a scale of 1-5, highest-ranked employees are 5). Write a sentence or two desribing what the plot tells you about the data. 
```{r}

```

## 5. BONUS: Create another plot of your choosing and then describe what you plotted and what the plot might tell us about the data. 