```{r}
REMOVE ME
```

---
title: "Assignment 6 - Classification"
author: "Lacey Hartigan"
date: "Due 3/30/21"
output:
  pdf_document: default
---

This problem set uses a kaggle.com dataset called: training_car.csv. Go to kaggle.com, search in the data section for "caravana" and download the training_car.csv dataset.

1. Calculate the proportion of lemons in the training dataset using the IsBadBuy variable.
```{r}
```

2. Calculate the proportion of lemons by Make. 
```{r}
```

3. Now, predict the probability of being a lemon using a linear model (`lm(y~x`), with covariates of your choosing from the training dataset (must have at least two covariates). 
```{r}
```

4. Make predictions from the linear model (in other words, add the predictions from your model to your dataset). Use head() to display the first 5-10 rows of data so I can see your variables. 
```{r}
```

5. Now, predict the probability of being a lemon using a logistic regression.
```{r}
```

6. Make predictions from the logit model. Make sure these are probabilities. Use head() to display the first 5-10 rows of data so I can see your variables. 
```{r}
```

7. Create a confusion matrix from your linear model and one from your logit model (and compare the two). 
```{r}
```

8. Plot the probability of a car being a bad buy by car make. 
```{r}
```

9. Create a table that shows the probability of a car being a bad buy by
make.
```{r}
```


Optional Bonus: Create a heatmap of the probability of a car being a bad buy by make and size. 
```{r}
```


